quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-15 paper-quollr.Rmd
Putting the implementation section earlier
Start updating the usage section

# Algorithm

@@

The `scurve` is a $7\text{-}D$ simulated dataset. It is constructed by simulating $1000$ observations from

$$
\begin{aligned}
\theta &\sim U(-3\pi/2, 3\pi/2), \\
X_1 &= \sin(\theta), \\
X_2 &\sim U(0, 2), \text{adding thickness to the S}, \\
X_3 &= \text{sign}(\theta) \times (\cos(\theta) - 1).
\end{aligned}
$$

The remaining variables $X_4$, $X_5$, $X_6$, and $X_7$ are included as low-magnitude noise dimensions, generated from uniform distributions with narrow ranges around zero: $X_4, X_5 \sim U(-0.02, 0.02)$, $X_6 \sim U(-0.1, 0.1)$, and $X_7 \sim U(-0.01, 0.01)$. These small variances ensure that the added dimensions contribute noise without obscuring the main geometric structure. `scurve_umap` is the UMAP \twoD embedding for `scurve` data with `n_neighbors`$=46$ and `min_dist`$=0.9$. Each data set contains a unique ID column that maps the $7\text{-}D$ point in `scurve` to the corresponding \twoD `scurve_umap`.

>>>>

@@

The `scurve` is a $7\text{-}D$ simulated dataset. It is constructed by simulating $1000$ observations.

`scurve_umap` is the UMAP \twoD embedding for `scurve` data with `n_neighbors`$=46$ and `min_dist`$=0.9$. Each data set contains a unique ID column that maps the $7\text{-}D$ point in `scurve` to the corresponding \twoD `scurve_umap`.

### 2025-10-15 paper-quollr.tex
Putting the implementation section earlier
Start updating the usage section

\section{Algorithm}\label{algorithm}

@@

The \texttt{scurve} is a \(7\text{-}D\) simulated dataset. It is constructed by simulating \(1000\) observations from

\[
\begin{aligned}
\theta &\sim U(-3\pi/2, 3\pi/2), \\
X_1 &= \sin(\theta), \\
X_2 &\sim U(0, 2), \text{adding thickness to the S}, \\
X_3 &= \text{sign}(\theta) \times (\cos(\theta) - 1).
\end{aligned}
\]

The remaining variables \(X_4\), \(X_5\), \(X_6\), and \(X_7\) are included as low-magnitude noise dimensions, generated from uniform distributions with narrow ranges around zero: \(X_4, X_5 \sim U(-0.02, 0.02)\), \(X_6 \sim U(-0.1, 0.1)\), and \(X_7 \sim U(-0.01, 0.01)\). These small variances ensure that the added dimensions contribute noise without obscuring the main geometric structure. \texttt{scurve\_umap} is the UMAP $2\text{-}D$ embedding for \texttt{scurve} data with \texttt{n\_neighbors}\(=46\) and \texttt{min\_dist}\(=0.9\). Each data set contains a unique ID column that maps the \(7\text{-}D\) point in \texttt{scurve} to the corresponding $2\text{-}D$ \texttt{scurve\_umap}.

>>>>

@@

The \texttt{scurve} is a \(7\text{-}D\) simulated dataset. It is constructed by simulating \(1000\) observations.

\texttt{scurve\_umap} is the UMAP $2\text{-}D$ embedding for \texttt{scurve} data with \texttt{n\_neighbors}\(=46\) and \texttt{min\_dist}\(=0.9\). Each data set contains a unique ID column that maps the \(7\text{-}D\) point in \texttt{scurve} to the corresponding $2\text{-}D$ \texttt{scurve\_umap}.
